### 2019-06-11 doc/chapters/introduction.tex
typo

With \textit{ensuring}, we define the postcondition of a function.
\textit{ensuring} is placed at the end of the function after the body.
\textit{ensuting} specifies, if the return value or the result of the function hold a certain condition.

@@

The function recursively calculates factorial of an integer number.
The input of the function is constrained with \textit{require} to a non-negative value.
The result should also be non-negative.
Thus, Stainless will verify whether the result of the factorial calculation is non-negative for all non-negative inputs.

@@

Let's return back to our incorrect example with factorial.
Stainless reports the following result for the factorial verification from our example:
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.5]{images/output1.png}
	\caption{Output of Stainless verification for calculating factorial of Int number}
	\label{fig:output1}
\end{figure}

@@

The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which allowed to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of the air.
Thus, we try to verify the property, that a non-coinbase transaction cannot generate new coins.
Lets name it the \nameref{property_1}.

@@

In Bitcoin-S there is a class Satoshis representing an amount of bitcoins.
We look at the verification of the addition of Satoshis with zero Satoshis.
This operation should result in the same amount of Satoshis.
Lets call it the \nameref{property_2}.

Using Stainless, we see the successfull verification of this property.
But the process of the verification with the tool requires many changes in the code, so that Stainless can accept it.
We look at all needed modifications in chapter \ref{chap:verify_add}.

>>>>

With \textit{ensuring}, we define the postcondition of a function.
\textit{ensuring} is placed at the end of the function after the body.
\textit{ensuring} specifies, if the return value or the result of the function hold a certain condition.

@@

It recursively calculates factorial of an integer number.
The input of the function is constrained with \textit{require} to a non-negative value.
The result should also be non-negative.
Thus, Stainless will verify whether the result of the factorial calculation is non-negative for all non-negative inputs.

@@

Let's return to our incorrect example with factorial.
Stainless reports the following result for the factorial verification from our example:
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.5]{images/output1.png}
	\caption{Output of Stainless verification for calculating factorial of Int number}
	\label{fig:output1}
\end{figure}

@@

The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which allowed to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of the air.
Thus, we try to verify the property, that a non-coinbase transaction cannot generate new coins.
Let's name it the \nameref{property_1}.

@@

In Bitcoin-S there is a class Satoshis representing an amount of bitcoins.
We look at the verification of the addition of Satoshis with zero Satoshis.
This operation should result in the same amount of Satoshis.
Let's call it the \nameref{property_2}.

Using Stainless, we see the successful verification of this property.
But the process of the verification with the tool requires many changes in the code, so that Stainless can accept it.
We look at all needed modifications in chapter \ref{chap:verify_add}.
